better title eventually

### 2015-05-11 cs261n-paper/paper.tex
Section on Tor.

\subsection{Tor} %%% 
\indent \indent Talk about anything relevant to Tor. Just enough background so
that people who have never heard of it will know what I am talking
about, but no more than that.

We don't want Tor to be like this, and want people to use it!

>>>>

\subsection{Tor} 
% \indent \indent Talk about anything relevant to Tor. Just enough background so
% that people who have never heard of it will know what I am talking
% about, but no more than that.

The Tor Project, known for its anonymity network~\cite{tor-design},
has in recent years become an important player in the world of
censorship circumvention.
In its early days, people used Tor to evade censorship,
and in response censors began to block Tor itself.
In response, work began on various anti-censorship technologies
now known as ``pluggable transports''~\cite{pluggable-transports}.
Currently there are over 15,000 users accessing the Tor network
at any given time using one of these
anti-censorship technologies~\cite{userstats-bridge-country}.

Tor Browser~\cite{tor-browser},
a specially modified version of Firefox that comes
with a built-in Tor proxy and pluggable transports,
is the primary means through which users access the Tor network.
It aims to make powerful anonymity and circumvention technology
accessible even to nontechnical users.
Its user interface was greatly overhauled in its version~3.5 release,
and since then it has not had a comprehensive usability evaluation.
